factor_explorer

### 2014-06-20 alex/2020.Rmd

>>>>

For each country, find the percentage of top 20% students in each school.
```{r math-sci-read}
school2020 = student2012 %>% 
              select(CNT, math, SCHOOLID) %>%
              group_by(CNT) %>%
              mutate(top20 = math > quantile(math, probs = seq(0, 1, 0.2))[5]) %>%
              group_by(CNT, SCHOOLID) %>%
              summarise(num_top20 = sum(top20), total_students = length(top20)) %>%
              mutate(pct_top20 = num_top20 / total_students)

```

### 2014-06-20 ijlyttle/factor_explorer.Rmd

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(shiny)

@@

# clean
rm(fn_make_df)
rm(item2012dict, parent2012dict, school2012dict, scoredItem2012dict, student2012dict)
```

@@

```{r shiny_variable_lists}
var_names_student <- dict_student2012$variable
names(var_names_student) <- 
  dict_student2012$description %>%
  str_replace_all("\x92", "'") # gets rid of funny characters"
```

```{r shiny_inputs}
selectInput(
  "test",
  "variable",
  choices = var_names_student
)
```

>>>>

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(shiny)
library(magrittr)

@@

# clean
rm(fn_make_df)
#rm(item2012dict, parent2012dict, school2012dict, scoredItem2012dict, student2012dict)
```

@@

```{r shiny_variable_lists}
var_names_student <- dict_student2012$variable
names(var_names_student) <- 
  dict_student2012$description %>%
  str_replace_all("\x92", "'") # gets rid of funny characters"

# using pv1 for now
var_names_student_subject <- c(
  math = "PV1MATH",
  science = "PV1SCIE",
  reading = "PV1READ"
)

var_names_student_type <- 
  lapply(student2012, class)

var_names_student_factor <- 
  var_names_student_type[var_names_student_type == "factor"] %>%
  names

tmp <- var_names_student_factor[var_names_student_factor == var_names_student] 
```

```{r shiny_inputs, echo = FALSE}
selectInput(
  "subject",
  label = "Subject",
  choices = var_names_student_subject
)

selectInput(
  "country",
  label = "Countries",
  choices = levels(student2012$CNT),
  selected = "Albania",
  multiple = TRUE
)

# selectInput(
#   "factor"
#   label = "Factor",
#   choices = 
# )
```

```{r shiny_transform, echo = FALSE}
rct_data <- reactive({
  df <- 
    student2012 %>%
    filter(CNT %in% input$country)

})

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(x = "factor(ST06Q01)", 
               y = input$subject), 
    scale = "width"
  )
})

```
